Inferring the gravitational potential of the Milky Way with a few precisely measured stars

### 2014-03-31 text/paper2/ms.tex
spacing
remove notes

% packages
\usepackage{amssymb,amsmath, amsbsy}
\usepackage{booktabs}
\usepackage[caption=false]{subfig}

@@

\begin{table}[h]
\begin{center}
	\begin{tabular}{l c l} \toprule
		\multicolumn{3}{l}{{\bf \emph{Milky Way parameters} ($\bs{\Theta}_\Phi$)}} \\
		\toprule
		Component & Parameter & Prior \\\toprule
		disk & $M_{\rm disk}$ & $1.0\times10^{11}\,\msun$ (fixed) \\ 
		& $a$ & 6.5 kpc (fixed)\\
		& $b$ & 0.26 kpc (fixed)\\
		\midrule
		spheroid & $M_{\rm spher}$ & $3.4\times10^{10}\,\msun$ (fixed)\\ 
		& $c$ & 0.7 kpc (fixed)\\
		\midrule
		halo & $\vhalo$ & $\mathcal{U}(100,200)$ km/s \\
		& $q_1$ & $\mathcal{U}(1,2)$\\
		& $q_2$ & 1.0 (fixed)\\
		& $q_z$ & $\mathcal{U}(1,2)$\\
		& $\phi$ & $\mathcal{U}(52,142)$ deg\\
		& $r_h$ & 12 kpc (fixed)\\
		\toprule
		\multicolumn{3}{l}{{\bf \emph{Progenitor parameters} ($\bs{\Theta}_\sat$)}} \\
		\toprule
		position & $\bs{r}_{\sat,0}$ & $\|\bs{r}_{\sat,0}\|\sim\mathcal{U}(0,200)$~kpc \\
		velocity & $\bs{v}_{\sat,0}$ & $\|\bs{v}_{\sat,0}\|\sim\mathcal{N}(\mu=0,\sigma^2=4000)$~km/s\\
		Lagrange pt. offset & $\alpha$ & $\mathcal{N}(\mu=2,\sigma^2=1)$\\
		initial mass & $m_0$ & $2.5\times10^8\,\msun$ (fixed)\\
		mass loss & $\dot{m}$ & $3.2\times10^4\,\msun$/Myr (fixed)\\
		\toprule
		\multicolumn{3}{l}{{\bf \emph{Star parameters} ($\bs{\Theta}^{(i)}$)}} \\
		\toprule
		position & $\bs{r}_0$ & $\|\bs{r}_0\|\sim\mathcal{U}(0,200)$~kpc \\
		velocity & $\bs{v}_0$ & $\|\bs{v}_0\|\sim\mathcal{N}(\mu=0,\sigma^2=4000)$~km/s\\
		tail assignment (binary) & $\beta$ & $\pm1$~equally likely (fixed at truth)\\ % TODO: how to say equal weight to -1 or 1?
		time unbound & $\tub$ & $\mathcal{U}(0,6.2)~Gyr$\\ % TODO: talk about \tint (integration time) in text!
		\bottomrule
		\end{tabular}
	\caption{Parameter values used in the experiments of Section~\ref{sec:experiments}. $\mathcal{N}$ is the normal (Gaussian) distribution, and $\mathcal{U}$ the uniform distribution. There are 11 parameters for the Milky Way potential, but only four are left free to vary; some parameters are fixed (denoted by ``(fixed)'') at the true values used in the N-body simulations that generated the fake data. The progenitor has nine parameters --- the position, $\bs{r}_{\rm p}$, and velocity, $\bs{v}_{\rm p}$, vectors each contain three components --- but only five are left free to vary. The sky coordinates (e.g., Galactic $l$, $b$) are assumed to be known with negligible uncertainty. Each star has eight associated parameters, five of which are allowed to vary. Sky coordinates are fixed, along with the tail assignment (whether the star belongs to the leading or trailing tail). For inference with eight stars, there are $4+5+8\times5=49$ free parameters. \label{tbl:params}}
\end{center}
\end{table}

>>>>

% packages
\usepackage{amssymb,amsmath,amsbsy}
\usepackage{booktabs}
\usepackage[caption=false]{subfig}

@@

\begin{table}[h]
\begin{center}
	\begin{tabular}{l c l} \toprule
		\multicolumn{3}{l}{{\bf \emph{Milky Way parameters} ($\bs{\Theta}_\Phi$)}} \\
		\toprule
		Component & Parameter & Prior \\\toprule
		disk & $M_{\rm disk}$ & $1.0\times10^{11}\,\msun$ (fixed) \\ 
		& $a$ & 6.5 kpc (fixed)\\
		& $b$ & 0.26 kpc (fixed)\\
		\midrule
		spheroid & $M_{\rm spher}$ & $3.4\times10^{10}\,\msun$ (fixed)\\ 
		& $c$ & 0.7 kpc (fixed)\\
		\midrule
		halo & $\vhalo$ & $\mathcal{U}(100,200)$ km/s \\
		& $q_1$ & $\mathcal{U}(1,2)$\\
		& $q_2$ & 1.0 (fixed)\\
		& $q_z$ & $\mathcal{U}(1,2)$\\
		& $\phi$ & $\mathcal{U}(52,142)$ deg\\
		& $r_h$ & 12 kpc (fixed)\\
		\toprule
		\multicolumn{3}{l}{{\bf \emph{Progenitor parameters} ($\bs{\Theta}_\sat$)}} \\
		\toprule
		position & $\bs{r}_{\sat,0}$ & $\|\bs{r}_{\sat,0}\|\sim\mathcal{U}(0,200)$~kpc \\
		velocity & $\bs{v}_{\sat,0}$ & $\|\bs{v}_{\sat,0}\|\sim\mathcal{N}(\mu=0,\sigma^2=4000)$~km/s\\
		Lagrange pt. offset & $\alpha$ & $\mathcal{N}(\mu=2,\sigma^2=1)$\\
		initial mass & $m_0$ & $2.5\times10^8\,\msun$ (fixed)\\
		mass loss & $\dot{m}$ & $3.2\times10^4\,\msun$/Myr (fixed)\\
		\toprule
		\multicolumn{3}{l}{{\bf \emph{Star parameters} ($\bs{\Theta}^{(i)}$)}} \\
		\toprule
		position & $\bs{r}_0$ & $\|\bs{r}_0\|\sim\mathcal{U}(0,200)$~kpc \\
		velocity & $\bs{v}_0$ & $\|\bs{v}_0\|\sim\mathcal{N}(\mu=0,\sigma^2=4000)$~km/s\\
		tail assignment (binary) & $\beta$ & $\pm1$~equally likely (fixed at truth)\\ 
		time unbound & $\tub$ & $\mathcal{U}(0,6.2)~Gyr$\\ 
		\bottomrule
		\end{tabular}
	\caption{Parameter values used in the experiments of Section~\ref{sec:experiments}. $\mathcal{N}$ is the normal (Gaussian) distribution, and $\mathcal{U}$ the uniform distribution. There are 11 parameters for the Milky Way potential, but only four are left free to vary; some parameters are fixed (denoted by ``(fixed)'') at the true values used in the N-body simulations that generated the fake data. The progenitor has nine parameters --- the position, $\bs{r}_{\rm p}$, and velocity, $\bs{v}_{\rm p}$, vectors each contain three components --- but only five are left free to vary. The sky coordinates (e.g., Galactic $l$, $b$) are assumed to be known with negligible uncertainty. Each star has eight associated parameters, five of which are allowed to vary. Sky coordinates are fixed, along with the tail assignment (whether the star belongs to the leading or trailing tail). For inference with eight stars, there are $4+5+8\times5=49$ free parameters. \label{tbl:params}}
\end{center}
\end{table}
